Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-08-23 analysis/report/effectiveness_report.Rmd
better plots

  plot_spline <-
    ggplot(timesincevax_effects)+
    geom_hline(aes(yintercept=1), colour='grey')+
    geom_line(aes(x=tstop-1, y=hr))+
    geom_ribbon(aes(x=tstop-1, ymin=hr.ll, ymax=hr.ul), alpha=0.2, colour="transparent")+
    facet_grid(cols=vars(model_name))+
    scale_x_continuous(
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_log10(
      breaks=c(0.125, 0.167, 0.25, 0.33, 0.5, 0.67, 1, 1.5, 2, 3, 4, 6, 8),
      sec.axis = dup_axis(name="Lower hazard after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    labs(
      x = "Days since first dose",
      y = "Hazard ratio"
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

@@

  plot_adjsurv <-
    ggplot(timesincevax_curve)+
    geom_step(aes(x=tstop, y=survival, group=vax1_az_descr, colour=vax1_az_descr))+
    geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=survival.ll, ymax=survival.ul, group=vax1_az_descr, fill=vax1_az_descr), alpha=0.1)+
    facet_grid(cols=vars(model_name))+
    scale_x_continuous(
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0)
    )+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x="Days since first dose",
      y="Adjusted survival",
      colour=NULL
    )+
    theme_bw()+
    theme(
      legend.position="bottom",
      legend.direction = "horizontal",
      axis.text.x.top=element_text(hjust=0),

      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

>>>>

  plot_spline <-
    ggplot(timesincevax_effects)+
    geom_hline(aes(yintercept=1), colour='grey')+
    geom_line(aes(x=tstop-1, y=hr))+
    geom_ribbon(aes(x=tstop-1, ymin=hr.ll, ymax=hr.ul), alpha=0.2, colour="transparent")+
    facet_grid(cols=vars(model_name))+
    scale_x_continuous(
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_log10(
      breaks=c(0.125, 0.167, 0.25, 0.333, 0.5, 0.667, 1, 1.5, 2, 3, 4, 6, 8),
      sec.axis = dup_axis(name="Lower hazard after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    labs(
      x = "Days since first dose",
      y = "Hazard ratio"
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

@@

  plot_adjsurv <-
    ggplot(timesincevax_curve)+
    geom_step(aes(x=tstop, y=survival, group=vax1_az_descr, colour=vax1_az_descr))+
    geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=survival.ll, ymax=survival.ul, group=vax1_az_descr, fill=vax1_az_descr), alpha=0.1)+
    facet_grid(cols=vars(model_name))+
    scale_x_continuous(
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0),
      limits = c(NA,1L)
    )+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x="Days since first dose",
      y="Adjusted survival",
      colour=NULL
    )+
    theme_minimal()+
    theme(
      legend.position="bottom",
      legend.direction = "horizontal",
      axis.text.x.top=element_text(hjust=0),

      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),
      axis.line.x.top = element_line(colour = "black"),
